I don't know, are you sure you want to do this?

### 2016-10-10 submission/paper.tex
Code for Bergen simulations. Inclusion of one picture in paper.

\subsection{Local sea level}
In order to get from global sea level projections to local ones, it is important to note that sea level rise not is uniform over the globe. Glacial and land ice melting affect the local sea level differently depending on where the melted ice is located.
%Gravitaional effects
Another major effect in Fennoskandia is the land rise due to isostatic rebound from the glaciers of the last ice age. 
Again, we will use historical data to relate global sea level to isostatically corrected local sea level using a time series regression model. 
%Figure showing corrected and uncorrected Bergen data and regression model.

@@

%Figure showing Bergen and Copenhagen slr projections

>>>>

\subsection{Local sea level}
In order to get from global sea level projections to local ones, it is important to note that sea level rise not is uniform over the globe. Glacial and land ice melting affect the local sea level differently depending on where the melted ice is located.
%Gravitaional effects
Another major effect in Fennoskandia is the land rise due to isostatic rebound from the glaciers of the last ice age. 
Again, we will use historical data to relate global sea level to isostatically corrected local sea level using a time series regression model. Figure \ref{fig:obs} shows uncorrected and corrected Bergen sea level data, and the relationship between the corrected Bergen data and the global sea level data. The time series regression uses an ARMA(1,1)-model \citep{boxjenkins}.
\begin{figure}
\begin{center}
\includegraphics[width=39pc]{bergenfit.png}
\caption{ The left figure shows raw (black)and gia-corrected (red) sea level data from Bergen, The right figure relates the gia-corrected Bergen sea level to the global sea level series of \citet{csiro}. The straight line is the time series regression line.}
\label{fig:obs}
\end{center}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[width=39pc]{bergen_ci.png}
\caption{ }
\label{fig:ci}
\end{center}
\end{figure}
